Model Recognition as Planning

### 2018-11-13 doc/icaps-19/model-recognition.tex
Updated evaluation section for blocks domain (WIP)

\subsection{Recognition of failures in non-deterministic {\em blocksworld} models}

>>>>

\subsection{Recognition of failures in {\em blocksworld} domain}
For our second experiments we have generated a set of observations for the {\em blocksworld} domain where some of the actions may fail. In more detail, the failures we consider are:

\begin{itemize}
	\item Stack fails and does nothing.
	\item Unstack fails and does nothing.
	\item Unstack fails and drops the block on the table.
\end{itemize}

We limited the errors to one type of error per observation, but it would be possible to recognize combinations of errors. The input models extend a 4-schemata {\em blocksworld} domain with an additional action schema that encodes one of the above failures. This means that the failure can be identified by finding the model that better explains the observation.

Our aim with this experiment is to validate the assumptions underlying our approximation of the $P(\mathcal{O}|\mathcal{M})$ likelihood.
